---
title_meta  : Chapter 2
title       : Springboard Yelp Analysis
description : "Springboard Yelp Analysis"
---
--- type:NormalExercise xp:100 skills:1,3  key:0d1199072c
## Exploring the Data

For this course the data comes in three separate data sets. 

- The first is labeled `reviews` and it contains a `user_id`, a `business_id` and a `star` review.
- The second is labeled `users` and it is a list of `user_id's` and `user_names's`
- The last is labeled `businesses` and it is a contains information about the businesses on yelp like the business location, category of food, number of reviews and average star review.

They have been loaded into the environment already and are ready to be explored!

*** =instructions
- Explore the `reviews` data set with `summary()` function.
- Explore the `users` data set with `summary()` function.
- Explore the `businesses` data set with `summary()` function.

*** =hint
- Don't forget to look at all three data sets

*** =pre_exercise_code
```{r,eval=FALSE}
load(url("http://s3.amazonaws.com/assets.datacamp.com/production/course_1073/datasets/Springboard_Yelp_ch1ex1.Rdata"))
```

*** =sample_code
```{r,eval=FALSE}
# Explore the `reviews` data set with `summary()` 
summary(___)

# Explore the `users` data set with `summary()` 
summary(___)

# Explore the `businesses` data set with `summary()` 
summary(___)
```

*** =solution
```{r,eval=FALSE}
# Explore the `reviews` data set with `summary()` 
summary(reviews)

# Explore the `users` data set with `summary()` 
summary(users)

# Explore the `businesses` data set with `summary()` 
summary(businesses)

```

*** =sct
```{r,eval=FALSE}
# first instruction
msg1 = "Did you remember to take a look at the `reviews` data set?"
#test_output_contains("summary(reviews)", incorrect_msg = msg1)
test_function("summary",args = c("object"), index = 1, incorrect_msg = msg1)

# second instruction
msg2 = "Did you remember to take a look at the `users` data set?"
#test_output_contains("summary(users)", incorrect_msg = msg2)
test_function("summary",args = c("object"),index = 2, incorrect_msg = msg2)

# third instruction
msg3 = "Did you remember to take a look at the `businesses` data set?"
#test_output_contains("summary(businesses)", incorrect_msg = msg3)
test_function("summary",args = c("object"), index = 3, incorrect_msg = msg3)

# General
test_error()
success_msg("Good job! We've seen a little more about the data so now let's move on!")

```


--- type:MultipleChoiceExercise xp:50 skills:1,3  key:f48b5ed8a3
## How Many Reviews?

Now that you have created a simplified data set and are almost ready to begin manipulating the reviews take a moment to explore the new data set and answer the following question.

Take a look at the data set `indian` with `str()` and see how many reviews does our data set contain?

*** =instructions
- 1456
- 980
- 1238
- 1563
  
*** =hint
- There first row form the `str()` output indicates how many rows are in this data set. There is one review per row!  

*** =pre_exercise_code
```{r,eval=FALSE}
load(url("http://s3.amazonaws.com/assets.datacamp.com/production/course_1073/datasets/indian.RData"))
```

*** =sct
```{r,eval=FALSE}
msg1 <- "Try again!"
msg2 <- "Not so good... Maybe have a look at the hint."
msg3 <- "Incorrect. Maybe have a look at the hint."
msg4 <- "Very good! You found the total. Let's start manipulating the star reviews!"
test_mc(correct = 4, feedback_msgs = c(msg1, msg2, msg3, msg4))
```
